% Do not chage this part
\begin{center}
  \textbf{{\Large ACKNOWLEDGEMENT}}\\[60pt]
\end{center}
\addcontentsline{toc}{chapter}{\textbf{\normalsize{\emph{ACKNOWLEDGEMENT}}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The text herein are only samples, change them to your taste
First and foremost we would like to offer our deepest gratitude to our supervisor, Professor Dr.\ Md.\ Abul Kashem Mia for introducing us to the fascinating world of bioinformatics, supporting us throughout the full session of our thesis with his patience and knowledge. He shared his wisdom with us in analyzing subject matters, valued our thinking approach to synthesize those topics and encouraged us at the time of disappointment. His invaluable guidance, deep insights and suggestions drove us towards better ways of thinking about the problem. One simply could not wish for a better or friendlier supervisor.  

We would like to sincerely thank Md. Arifuzzaman and Md. Shazibul Islam Shamim, who have previously worked in this particular field and shared the primitive study materials and gave effective guidelines whenever we needed. The level of patience and time given by them is really praiseworthy.

Finally, we want to dedicate the essence of our purest respect to our parents who have made our existences possible. They always believed in us even at the moment when we were losing our believes in ourselves. It is not really we who reached here but of course it is our kind parents who gave us hope and inspiration.

\vspace*{20.0mm}

\begin{minipage}[t]{0.2\textwidth}
  Dhaka\par
  \thesisdate
\end{minipage}%
\hfill
\begin{minipage}[t]{0.45\textwidth}
  \begin{enumerate}
    \vspace{-0.75\baselineskip}
    \DTLforeach{ThesisStudents}{\StudentName=Column1}{\item[]\StudentName}
  \end{enumerate}
\end{minipage}

\endinput
